Annual Analysis of Delays in TTC Streetcars for the year 2023

### 2024-09-26 paper/paper.qmd
Updated llm usage.txt and removed unused files/folders

# Grouping and summarizing the data
grp_data <- data |> 
  group_by(line) |>
  summarise(average_delay = mean(min_delay), .groups = 'drop')

@@

# Filter the data for times between 08:00 and 01:00 i.e day shift
avg_delay_day_shift <- data |> 
  group_by(hour) |>
  summarise(average_delay = mean(min_delay), .groups = 'drop') |>
  filter(hour >= "08" | hour <= "01")

@@

# Filter the data for times between 02:00 and 07:00 i.e night shift
avg_delay_night_shift <- data |> 
  group_by(hour) |>
  filter(hour >= "02" & hour <= "07") |>
  summarise(average_delay = mean(min_delay), .groups = 'drop')

@@

freq_incidence <- data |> 
  group_by(incident) |> 
  summarise(frequency = n(), .groups = 'drop')

@@

delay_by_season <- data |>
  group_by(season) |>
  summarise(average_delay = mean(min_delay), .groups = 'drop')

>>>>

# Grouping and summarizing the data
grp_data <- data |> 
  group_by(line) |>
  summarise(average_delay = mean(min_delay))

@@

# Filter the data for times between 08:00 and 01:00 i.e day shift
avg_delay_day_shift <- data |> 
  group_by(hour) |>
  summarise(average_delay = mean(min_delay)) |>
  filter(hour >= "08" | hour <= "01")

@@

# Filter the data for times between 02:00 and 07:00 i.e night shift
avg_delay_night_shift <- data |> 
  group_by(hour) |>
  filter(hour >= "02" & hour <= "07") |>
  summarise(average_delay = mean(min_delay))

@@

freq_incidence <- data |> 
  group_by(incident) |> 
  summarise(frequency = n())

@@

delay_by_season <- data |>
  group_by(season) |>
  summarise(average_delay = mean(min_delay))
